CTest Integration of Sikuli Automated GUI Testing

### 2011-06-21 Documentation/Article.tex
Filled in Unit Testing subsection with verbatim def script.

% I'll write it this part
One of Sikuli's primary uses is the automation of GUI testing for software
developers. For GUI testing, it is useful to compartmentalize different software
functions and test each unit individually.\\

@@

Here we connect this Unit Testing feature to CTest, this allows us to report
results on public dashboard using CDash. To this end, we developed cmake
functions to discover where Sikuli is installed and special function to add
sikuli test in the list of test for CTest.

@@

Users can either maintain an image library, either keep images in the
corresponding sikuli script directory (default). If one use an image library,
the corresponding path must be set during CMake time in
the SIKULI\_IMAGE\_LIBRARY\_DIR variable.

@@

Sikuli's integration with CTest has provided us with numerous advantages in the
measure of productivity and convenience. But our goals are still
hindered by a few limitations.
%\subsection{Text Recognition}
%Sikuli's newer versions come equipped with a text recognition feature whereby
%one can search for a string of text instead of searching for the image of the
%text in the GUI.  This makes programming in Sikuli much simpler but it is
%limited by it's searchable text fonts.
\subsection{Off-screen Rendering}
Our goal in using CTest is that we will be able to test our software
automatically every night and bugs can be reported the next day on CDash.  But
Sikuli is not easily compatible with off-screen rendering.  Sikuli requires
that the screen remains on so that the script can identify the images on the
screen.  In addition, external mouse and keyboard actions can disrupt the script
at any moment.  These factors make it more difficult to set up automated
nightly tests.  
\subsection{Variation of style between machines}
%Different OS, different look => failures
%Even on the same OS, GUI can look different = > failures
Another important issue is the difference between operating systems. 
Developers need to make sure that their software runs on each
OS.  But Different operating systems require different libraries for
generating GUI images. Therefore fonts, icons, and even
layouts will differ between machines. This is also true between versions of the
same OS. So, GUI tests that pass on one machine will inevitably fail on another
machine for the same exact software. This requires developers to write the
same Sikuli script using images from each OS, which will be many times the
workload.  
\subsection{CDash}

>>>>

\subsection{CMake}

One of Sikuli's primary uses is the automation of GUI testing for software
developers. For GUI testing, it is useful to compartmentalize different software
functions and test each unit individually.\\

@@

Here we connect this Unit Testing feature to CTest, which allows us to report
results on a public dashboard using CDash. To this end, we developed cmake
functions to discover where Sikuli is installed and special functions to add
Sikuli tests in the list for CTest.

@@

Users can either maintain an image library or keep images in the
corresponding Sikuli script directory (default). If one uses an image library,
the corresponding path must be set during CMake time in
the SIKULI\_IMAGE\_LIBRARY\_DIR variable.

\subsection{Unit Test Script Format}

Unit testing scripts are written as a series of functions defined by pythons
keyword def.  The constructing and destructing methods,
\emph{setUp}() and \emph{tearDown}(), are used to start and end the software
GUI and methods in between are named with the prefix test.

\begin{verbatim}
def setUp(self):
  print "setUp";

def testPrint(self):
  print "dummy test to validate, it is printing on the screen!";

def tearDown(self):
  print "tearDown";
\end{verbatim}

When this script is run with the Sikuli Unit Testing feature, it will report the
results of each test method in CTest and then reported automatically on
CDash.

@@

Sikuli's integration with CTest has provided us with numerous advantages in the
measure of productivity and convenience. But our goals are still
hindered by a few limitations.
%\subsection{Text Recognition}
%Sikuli's newer versions come equipped with a text recognition feature whereby
%one can search for a string of text instead of searching for the image of the
%text in the GUI.  This makes programming in Sikuli much simpler but it is
%limited by it's searchable text fonts.
\subsection{Off-screen Rendering}
Our goal in using CTest is that we will be able to test our software
automatically every night and bugs can be reported the next day on CDash.  But
Sikuli is not easily compatible with off-screen rendering.  Sikuli requires
that the screen remains on so that the script can identify the images on the
screen.  In addition, external mouse and keyboard actions can disrupt the script
at any moment.  These factors make it more difficult to set up automated
nightly tests.  
\subsection{Variation of style between machines}
%Different OS, different look => failures
%Even on the same OS, GUI can look different = > failures
Another important issue is the difference between operating systems. 
Developers need to make sure that their software runs on each
OS.  But Different operating systems require different libraries for
generating GUI images. Therefore fonts, icons, and even
layouts will differ between machines. This is also true between versions of the
same OS. So, GUI tests that pass on one machine will inevitably fail on another
machine for the same exact software. This requires developers to write the
same Sikuli script using images from each OS, which will be many times the
workload.

\subsection{CDash}
Furthermore, CDash does not currently support Sikuli script since images used
in the script are unable to be displayed on the dashboard.  Without these
images on CDash, visualize which units are being tested.  In addition, CDash
does not make the distinction between simple syntax errors versus a complete
test failure. These are
extensions to CDash that can be corrected for future work.
